---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mediacloud

<!-- badges: start -->
<!-- badges: end -->

R wrapper package for the [MediaCloud](https://mediacloud.org/) API.

## Installation

You can install the development version of mediacloud from GitHub with:

```{r eval=FALSE}
#install.packages("remotes")
remotes::install_github("joon-e/mediacloud")
```


## Usage

```{r}
library(mediacloud)
```

### Authentication

Register for a MediaCloud account [here](https://explorer.mediacloud.org/#/user/signup). The API key can be passed directly to functions with the `key` argument. If no key is provided, then the package will look for one in the environment variable `MEDIACLOUD_API_KEY`. Thus, the easiest way to authenticate is to store your key using `Sys.setenv()`:

```{r eval=FALSE}
Sys.setenv(MEDIACLOUD_API_KEY = "YOUR_KEY_GOES_HERE")
```

### Search media

Search for media outlets with `search_media()`:

```{r cars}
search_media(tag = "Germany___National", n = 10)
```

This is mainly useful for matching media outlets with their MediaCloud `media_id`.

### Search stories

Search for stories with `search_stories()`:

```{r}
stories <- search_stories(title = "dogecoin", media_id = c(19831, 38697), after_date = "2021-05-01")
stories
```
The function provides a simplified interface for writing the [Solr queries](https://mediacloud.org/support/query-guide/) that MediaCloud parses to search for stories (`q` and `fq` parameters in the API call). This includes the following optional arguments:

- `text` and `title`: Character vector passed to full text search and title-only search, respectively. If the character vector contains more than one element, they will be connected with `OR` in the call.
- `media_id`: Limit to stories from media outlets with these `media_id`
- `after_date` and `before_date`: Limit to stories published after/before these dates. Should be a date string that can be interpreted as a `POSIXct` object, e.g., `"2021-01-01"` or `"2021-12-24 09:00:00"`. Note that `00:00:00` will be added if only passing a date, but no time, and boundaries are inclusive, so setting `after_date` to `"2021-01-01"` will include stories published at `2021-01-01 00:00:00` and later.

Use the argument `n` to control the maximum number of results returned with one call (`<= 1000`). Note that the returned object also includes the `processed_stories_id`, which can be passed to the argument `last_processed_stories_id` to paginate over results.

### Get word matrices

Get [Tidytext](https://juliasilge.github.io/tidytext/)-style word matrices associated with those stories with `get_word_matrices()`. This uses the same arguments as `search_stories()`, but is most useful to obtain word matrices for stories found with `search_stories()`:

```{r}
wm <- get_word_matrices(stories_id = stories$stories_id)
wm
```
The word matrices can be tranformed to Quanteda-style DFMs using `tidytext::cast_dfm()`:

```{r}
tidytext::cast_dfm(wm, stories_id, word_stem, word_counts)
```
